---
title: "Handling threedots input in batch scenarios"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{README}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(crudr)
run <- FALSE
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```

# Problem

Function that take their main arguments via `...` are great for interactive use, but sometimes a bit inconvenient when you want to do stuff in a batch manner.

## Simple example

Interactive mode:

```{r, eval=run}
library(settings)
x <- options_manager(a = 1, b = 2)
x()
```

Batch mode:

Suppose that `values` has been created by another upstream function and that you would like to feed that to `options_manager`.

```{r, eval=run}
values <- list(a = 1, b = 2)
x <- options_manager(values)
x()
```

Possibly not quite the value we would expect.

# Solution

## Simple draft 

The key is to implement a function that handles values passed via `...`.

Let's start out with a simple example:

```{r, eval=run}
foo <- function(...) {
  values <- list(...)
  nms <- names(values)
  if (is.null(nms)) {
    ## --> wrapped into list for batch setting
    do.call(options_manager, unlist(values, recursive = FALSE))
  } else if (any(idx <- nms == "")) {
    ## --> mixed
    values <- c(values[!idx], unlist(values[idx], recursive = FALSE))
    do.call(options_manager, values[sort(names(values))])
  } else {
    ## --> regular
    options_manager(...)
  }
}
```

That gives you the desired result no matter in what format you provide your input to `settings::options_manager`

```{r, eval=run}
opts <- foo(a = 1, b = 2)
opts()
opts <- foo(list(a = 1, b = 2))
opts()
opts <- foo(list(a = 1), b = 2)
opts()
```

## Generic proposal

This draft is a bit more generic.

- `handleThreedots` takes care of transforming values that came in via `...` so they are in the typical format that downstream functions taking their main input via `...` would expect.

- `withHandledThreedots` is simply a generic wrapper that combines calls to `handleThreedots` and the actual target function - which would be `settings::options_manager` in our example case.

```{r, eval=run}
handleThreedots <- function(...) {
  values <- list(...)
  nms <- names(values)
  if (is.null(nms)) {
    ## --> wrapped into list for batch setting
    unlist(values, recursive = FALSE)
  } else if (any(idx <- nms == "")) {
    ## --> mixed
    c(values[!idx], unlist(values[idx], recursive = FALSE))
    ## --> note that I did not introduce any sorting as before 
    ##     in order to not slow things down additionally 
  } else {
    ## --> regular
    values
  }
}
withHandledThreedots <- function(..., fun) {
  do.call(fun, handleThreedots(...))
}
```

Examples with only `handleThreedots`

```{r, eval=run}
handleThreedots(a = 1, b = 2, c = 3, d = 4)
handleThreedots(list(a = 1, b = 2), list(c = 3, d = 4))
handleThreedots(list(a = 1), b = 2, list(c = 3), d = 4)
```

Actual example:

```{r, eval=run}
res <- withHandledThreedots(a = 1, b = 2, c = 3, d = 4, 
  fun = options_manager)
res()
res <- withHandledThreedots(list(a = 1, b = 2), list(c = 3, d = 4),
  fun = options_manager)
res()
res <- withHandledThreedots(list(a = 1), b = 2, list(c = 3), d = 4,
  fun = options_manager)
res()
```

This approach can also handle additional arguments that `fun` might take:

```{r, eval=run}
res <- withHandledThreedots(a = 1, b = 2, c = 3, d = 4,
  fun = options_manager, .allowed = list(a = inrange(1, 2)))
res()
try(res(a = 3))
res <- withHandledThreedots(list(a = 1, b = 2), list(c = 3, d = 4),
  fun = options_manager, .allowed = list(a = inrange(1, 2)))
res()
try(res(a = 3))
res <- withHandledThreedots(list(a = 1), b = 2, list(c = 3), d = 4,
  fun = options_manager, .allowed = list(a = inrange(1, 2)))
res()
try(res(a = 3))
```

Just to make sure that the additional argument `.allowed` of `settings::options_manager` was simply not shown because its name starts with a dot

```{r, eval=run}
foo <- function(..., special = FALSE) {
  if (special) {
    message("hello world!")
  }
  list(...)
}
withHandledThreedots(a = 1, b = 2, c = 3, d = 4, fun = foo)
withHandledThreedots(a = 1, b = 2, c = 3, d = 4, fun = foo, special = TRUE)
```
